---
title: "WattTime Intro"
output: html_notebook
---

```{r}
library(tidyverse)
library(httr2)
library(jsonlite)
```

Register for WattCarbon API

Python3 API call

import requests
register_url = 'https://api2.watttime.org/v2/register'
params = {'username': 'freddo',
         'password': 'the_frog',
         'email': 'freddo@frog.org',
         'org': 'freds world'}
rsp = requests.post(register_url, json=params)
print(rsp.text)


ONLY RUN ONCE!
```{r eval=FALSE, include=FALSE}

#Sys.setenv(watttime_pw = '***')

watttime_pw <- Sys.getenv("watttime_pw")

req <- request('https://api2.watttime.org/v2/register') %>% 
  req_body_json(list('username' = 'jedlovec3', 
              'password' = watttime_pw ,
              'email' = 'ben.jedlovec+watttime@gmail.com',
              'org' = 'self'))

#req %>% req_dry_run()

resp <- req_perform(req)
resp_json <- resp %>% resp_body_json()
data_df <- as.data.frame(resp_json)
data_df
```


Login & Obtain Token

Python3 Example
login_url = 'https://api2.watttime.org/v2/login'
rsp = requests.get(login_url, auth=HTTPBasicAuth('freddo', 'the_frog'))

```{r}
req <- request('https://api2.watttime.org/v2/login') %>% 
  req_auth_basic("jedlovec3", watttime_pw)

resp <- req_perform(req)
resp_json <- resp %>% resp_body_json()
data_df <- as.data.frame(resp_json)
data_df

api_token <- data_df$token

api_token
```
Basic Request for accessible 

login_url = 'https://api2.watttime.org/v2/login'
token = requests.get(login_url, auth=HTTPBasicAuth('freddo', 'the_frog')).json()['token']

list_url = 'https://api2.watttime.org/v2/ba-access'
headers = {'Authorization': 'Bearer {}'.format(token)}
params = {'all': 'false'}
rsp=requests.get(list_url, headers=headers, params=params)
print(rsp.text)

```{r}

req <- request('https://api2.watttime.org/v2/ba-access') %>% 
  req_headers(Authorization = paste("Bearer", api_token)) %>% 
  req_url_query('all' = 'false')

resp <- req_perform(req)

#resp %>% resp_body_json()

resp_json <- resp %>% resp_body_json()
data_df <- as.data.frame(resp_json)
data_df

#resp %>% resp_headers()


```


```{r}

req <- request('https://api2.watttime.org/v2/ba-access') %>% 
  req_headers(Authorization = paste("Bearer", api_token)) %>% 
  req_url_query('all' = 'true')

resp <- req_perform(req)

#resp %>% resp_body_json()

resp_json <- resp %>% resp_body_json()
data_df <- as.data.frame(resp_json)
data_df

```

Formatting gets weird if returning multiple responses in JSON
- Will need to investigate in future

```{r}

req <- request('https://api2.watttime.org/index') %>% 
  req_headers(Authorization = paste("Bearer", api_token)) %>% 
  #req_url_query('ba' = 'PJM_NJ')
  req_url_query('ba' = 'CAISO_NORTH')

resp <- req_perform(req)

#resp %>% resp_body_json()

resp_json <- resp %>% resp_body_json()
data_df <- as.data.frame(resp_json)
data_df

```

```{r}

```


